Copykat CNV results exploration for `r params$sample_id`

### 2024-10-15 analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

---
title: "Copykat CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  sample_id: "SCPCS000194"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

>>>>

---
title: "Copykat CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  sample_id: "SCPCS000194"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---
